---
title: "gpelose_OriginalHomeworkCode_01"
author: "Greg Pelose"
date: "9/11/2019"
output: html_document
---
# Copying and Pasting RAW data into atom and also installed stringr to this R project.

```{r}
library("stringr")
```

#Creating a vecotr of one word characters from the first line of the book Ulysses.

```{r}
v<-c("Stately", "plump", "buck", "Mulligan", "came", "from", "the", "stairhead,", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed.")
```

#Now I want to extract every third element of this vector 


```{r}
str_extract(v, "buck")
str_extract(v, "from")
str_extract(v, "bearing")
str_extract(v, "of")
str_extract(v, "which")
str_extract(v, "and")
str_extract(v, "lay")
```

#Creating Matrix 

```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
```

# naming rows and columns of matrix (m)

```{r}
rownames(m) <-c("r1", "r2", "r3", "r4", "r5", "r6", "r7", "r8")
colnames(m) <-c("c1", "c2", "c3", "c4", "c5", "c6", "c7", "c8", "c9", "c10")
```

#I just found out that I did not want to name them so starting back to creating the matrix.

```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
```

#selecting specific column and rows and assigning them to a variable. First I will name the 2nd 3rd and 6th column, c2, c3, and c6 

```{r}
c2 <- m[,2]
c3 <- m[,3]
c6 <- m[,6]
```

#Now I will attempt to put all of these under the variable x
#this did not work, I will now try and make a new matrix using the assingned names. 

```{r}
m[c(c2, c3, c6)]
```

#Now I will assign them to the variable x

```{r}
x <- m[c(c2, c3, c6)]
```

#now I will extract the 6th to 8th row by naming each row r6, r7 and r8, creating a new matrix with these variables, followed by assigning them to the variable x

```{r}
r6 <- m[6,]
r7 <- m[7,]
r8 <- m[8,]
```

```{r}
x <- m[c(r6, r7, r8)]
```

#I will now do the same thing for part three of challenge 2 where I will extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x

```{r}
c9 <- m[,9]
r2 <- m[2,]
```

#I already have row 6 and column 2 assigned. I added c9 and r2

```{r}
x <- m[c(r2, c2, r6, c9)]
```

#Challenge 3 
# I am going to Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series).

```{r}
a <- array(data=1:400,dim=c(5,5,4,4))
```

#Next step of the challenge: Given this matrix, what would the following return?

```{r}
a[1, 1, 1, 2]
```

#this returned with a value of 101

```{r}
a[2, 3, 2, ]
```

#This returned with these values 37 137 237 337

```{r}
a[1:5, 1:5, 3, 3]
```

#Below is what was returned when thee values were plugged in. 

#I stated the above in my original homework because I did not know you could run code in this document. 

#Challenge 4, Creating a list 

```{r}
a <- "Primates"
b <- "Haplorhini"
c <- "Anthropoidea"
d <- "Platyrrhini"
e <- "Cebidae"
f <- "Atelidae"
g <- "Pitheciidae"
h <- "Catarrhini"
i <- "Cercopithecidae"
j <- "Hylobatidae"
k <- "Hominidae"
l <- "Tarsioidea"
m <- "Tarsiidae"
n <- "Strepsirhini"
o <- "Lorisoidea"
p <- "Lorisidae"
q <- "Galagidae"
r <- "Lemuroidea"
s <- "Cheirogaleidae"
t <- "Lepilemuridae"
u <- "Indriidae"
v <- "Lemuridae"
w <- "Daubentoniidae"
```

#This is a list of all of the names but I cannot figure out how to get them into a specific order

```{r}
list(a,b,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w)
```

#I condensed the lists to attempt to make them in the correct order as the list online. This makes sense in my head but I am not positive that this is correct. 

```{r}
list(a,b,c,d)
list(c(e,f,g))
list(h)
list(c(i,j,k))
list(l)
list(m)
list(n)
list(o)
list(c(p,q))
list(r)
list(c(s,t,u,v,w))
```

#Challenge 5

```{r}
matrix(data=c(3,0,1,23,1,2,33,1,1,42,0,1,41,0,2),nrow=5,ncol=3,byrow=TRUE)
```

#following this names my matrix

```{r}
MATRIX1 <-matrix(data=c(3,0,1,23,1,2,33,1,1,42,0,1,41,0,2),nrow=5,ncol=3,byrow=TRUE)
```

#following this I Coerced this matrix into a data frame and named it M1data

```{r}
M1data <- as.data.frame(MATRIX1)
```

#Now I am going to try and coerce the second column to be logical-valued and then try to coerce the third column to be factor-valued

```{r}
as.logical(M1data$V2)
```

#above states the information from column 2 in logical form
#then I replaced the old V2 with a new V2 that is in logical form in the data frame.

```{r}
V2 <-as.logical(M1data$V2)
M1data$V2<-V2
```

#now I am going to attempt to coerce the third column to be factor-valued. Factor 1 will be hawkfish and factor 2 will be clownfish

```{r}
v3 <- as.factor(M1data$V3)
```

#above states me attempting to represent column 3 as a factor.
#next I changed this column with my new factor column.  
```{r}
M1data$V3<-v3
```

#following this I changed the name of the levels involved with my factor to hawkfish and blenny becasue those are two of my favorite fish that are common in the aquarium trade. 

```{r}
levels(M1data$V3)[2]<-"hawkfish"
levels(M1data$V3)[1]<-"blenny"
```

#at this point, pplugging in M1data will show that I have changed the variables!

```{r}
str(M1data)
```

#PROBLEMS

1. My first problem is organizing all of my codes, I still am not sure if I did this correctly as it all seems jumbled up.

2. I struggled creating the list and trying to get it to look the same way as the list online, I feel like this is not possible and I am overthinking it. I spent way to much time on that section trying to learn how to create the list with lists inside of the lists. 

3.looking back at the first challenge. I still am not sure if I did this correctly as I have extracted every third one but I could not figure out how to do this with one single fuunction. I feel like there is some way to extract every 3rd variable with a single function but I could not figure it out.

4. I struggled to try and figure out how to select certain columns of each matrix. I tried naming all of the rowns and columns thinking that would help but it did not.

5. I had trouble with opening a project in R-studio and then getting it to push back to git-hub at first. This took me a while to figure out. I was struggling with copying the lines of code from github and then using that in R, that seemed very confusing at first but I firgured it out eventually. 

